Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-10 manuscript.tex
Add bibliography

Due to the high pitch angles experienced by the H$^2$Bird, we use a 
quaternion representation of vehicle pose to avoid the numerical 
instabilities of Euler angle representations. This choice of pose 
representation also lends itself well to remote guidance, as relative body 
and world coordinate angular displacements can be represented compactly 
with quaternion multiplication.

@@

%%
%% The following two commands are all you need in the
%% initial runs of your .tex file to
%% produce the bibliography for the citations in your paper.
%\bibliographystyle{abbrv}
%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this 
% case
%% You must have a proper ".bib" file
%%  and remember to run:
%% latex bibtex latex latex
%% to resolve all references
%%
%% ACM needs 'a single self-contained file'!
%%
%%APPENDICES are optional
%%\balancecolumns
%\appendix
%%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%% This next section command marks the start of
%% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The aamas2013 .cls file is based on the
%sig-alternate.cls file that is itself chock-full of succinct and
%helpful comments.  If you consider yourself a moderately experienced
%to expert user of \LaTeX, you may find reading it useful but please
%remember not to change it.
%%\balancecolumns % GM June 2007
%% That's all folks!
\end{document}

>>>>

Due to the high pitch angles experienced by the H$^2$Bird, we use a 
quaternion representation of vehicle pose to avoid the numerical 
instabilities of Euler angle representations. This choice of pose 
representation also lends itself well to remote guidance, as relative body 
and world coordinate angular displacements can be represented compactly 
with quaternion multiplication.~\cite{bowman:reasoning}

@@

%%
%% The following two commands are all you need in the
%% initial runs of your .tex file to
%% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{manuscript}

%% You must have a proper ".bib" file
%%  and remember to run:
%% latex bibtex latex latex
%% to resolve all references
%%
%% ACM needs 'a single self-contained file'!
%%
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
%The aamas2013 .cls file is based on the
%sig-alternate.cls file that is itself chock-full of succinct and
%helpful comments.  If you consider yourself a moderately experienced
%to expert user of \LaTeX, you may find reading it useful but please
%remember not to change it.
%%\balancecolumns % GM June 2007
\end{document}
